Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
Ancho de banda con AWS y rCUDA añadido

\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{AWS available HPC instances}
\label{table:awsInstances}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccccc}
Name & vCPUs & Memory & Network & GPUs & Price\\ \hline \hline
c3.2xlarge & 8 & 15 GiB & High & 0 & \$ 0.21\\ \hline
c3.8xlarge & 32 & 60 GiB & 10 Gb & 0 & \$ 1.68 \\ \hline
g2.2xlarge & 8 & 15 GiB & High & 1 & \$ 0.65\\ \hline
g2.8xlarge & 32 & 60 GiB & 10 Gb & 4 & \$ 2.6 \\ \hline
\end{tabular}\end{center}\end{table}

@@

\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{IPERF results between instances}
\label{table:iperf}
\tabcolsep=0.24cm
\begin{center}\begin{tabular}{cccc}
Server & Client & Network & Bandwidth\\ \hline \hline
g2.8xlarge & c3.2xlarge & High & 1  Gb/s\\ \hline
g2.8xlarge & c3.8xlarge & 10Gb & 7.5  Gb/s\\ \hline
g2.8xlarge & g2.2xlarge & High & 1 Gb/s\\ \hline
g2.8xlarge & g2.8xlarge & 10Gb & 7.5  Gb/s\\ \hline
\end{tabular}\end{center}\end{table}

@@

\subsubsection{GPUs}
As it has been said before, an instance is based in a VM 
which is running on a real node with its own virtualized 
components, so it is possible that AWS could use a virtualization 
framework to offer GPU services to all the instances.
Therefore, we need to verify if the GPUs showed in the instances are 
non-virtualized GPUs so, we have executed the NVIDIA SDK test called 
{\tt bandwidthtest}. As it is shown in the Table~\ref{table:bwt}, as the bandwidth achieved 
in this test is higher than the network bandwith, it reveals that it is a 
real GPU. 
\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transfering 32MB using pageable memory }
\label{table:bwt}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Name &  Data Movement & Network & BandWidth \\ \hline \hline
g2.2xlarge & Host to Device & Hight& 3,004 MB/s \\ \hline
g2.2xlarge & Device to Host & Hight& 2,809 MB/s\\ \hline
g2.8xlarge & Host to Device & 10 Gb& 2,814 MB/s\\ \hline
g2.8xlarge & Device to Host & 10 Gb& 3,182 MB/s\\ \hline
\end{tabular}\end{center}\end{table}

@@

\begin{figure*}[ht]
\centering
\subfigure[5 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws3.png}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws2.png}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws1.png}
\label{subfig:aws3}}
\caption{Different configurations where an AWS instance acting as a client is using several remote GPUs}
\label{fig:aws}
\end{figure*}

@@

The first of them was {\it Montecarlo Multigpu} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of Figure~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.
% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{Montecarlo options per second}
  \label{fig:mont-opt}
\end{figure}

>>>>

\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{AWS available HPC instances.}
\label{table:awsInstances}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccccc}
Name & vCPUs & Memory & Network & GPUs & Price\\ \hline \hline
c3.2xlarge & 8 & 15 GiB & High & 0 & \$ 0.21\\ \hline
c3.8xlarge & 32 & 60 GiB & 10 Gb & 0 & \$ 1.68 \\ \hline
g2.2xlarge & 8 & 15 GiB & High & 1 & \$ 0.65\\ \hline
g2.8xlarge & 32 & 60 GiB & 10 Gb & 4 & \$ 2.6 \\ \hline
\end{tabular}\end{center}\end{table}

@@

\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{IPERF results between instances.}
\label{table:iperf}
\tabcolsep=0.24cm
\begin{center}\begin{tabular}{cccc}
Server & Client & Network & Bandwidth\\ \hline \hline
g2.8xlarge & c3.2xlarge & High & 1  Gb/s\\ \hline
g2.8xlarge & c3.8xlarge & 10Gb & 7.5  Gb/s\\ \hline
g2.8xlarge & g2.2xlarge & High & 1 Gb/s\\ \hline
g2.8xlarge & g2.8xlarge & 10Gb & 7.5  Gb/s\\ \hline
\end{tabular}\end{center}\end{table}

@@

\subsubsection{GPUs}
As it has been said before, an instance is based in a VM 
which is running on a real node with its own virtualized 
components, so it is possible that AWS could use a virtualization 
framework to offer GPU services to all the instances.
Therefore, we need to verify if the GPUs showed in the instances are 
non-virtualized GPUs so, we have executed the NVIDIA SDK test called 
{\tt bandwidthtest}. As it is shown in the Table~\ref{table:bwt}, as the bandwidth achieved 
in this test is higher than the network bandwith, it reveals that it is a 
real GPU. 
\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transfering 32MB using pageable memory using local GPU.}
\label{table:bwt}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Name &  Data Movement & Network & BandWidth \\ \hline \hline
g2.2xlarge & Host to Device & Hight& 3,004 MB/s \\ \hline
g2.2xlarge & Device to Host & Hight& 2,809 MB/s\\ \hline
g2.8xlarge & Host to Device & 10 Gb& 2,814 MB/s\\ \hline
g2.8xlarge & Device to Host & 10 Gb& 3,182 MB/s\\ \hline
\end{tabular}\end{center}\end{table}

@@

\begin{figure*}[ht]
\centering
\subfigure[5 remote GPUs over 1GbE.]{%
\includegraphics[width=0.31\linewidth]{images/aws3.png}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE.]{%
\includegraphics[width=0.31\linewidth]{images/aws2.png}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE.]{%
\includegraphics[width=0.31\linewidth]{images/aws1.png}
\label{subfig:aws3}}
\caption{Different configurations where an AWS instance acting as a client is using several remote GPUs.}
\label{fig:aws}
\end{figure*}

Once the scenarios are configured from the point of view of hardware, 
the {rCUDA} software needs to be installed in order to add 
the required flexibility to the system. So, the {rCUDA} server has been 
executed in the server nodes and the {rCUDA} libraries have been installed 
in the node that is acting as a client.

Moreover, with the aim to know the expected network bandwidth using 
a remote GPU, we have executed again the NVIDIA {\tt bandwidthtest} sample.
The results observed in the Table~\ref{} shows how the bandwidth achieved is limited 
by the network.

\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transfering 32MB using pageable memory using {rCUDA}.}
\label{table:bwt}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Scenario &  Data Movement & Network & BandWidth \\ \hline \hline
A & Host to Device & Hight& 127 MB/s \\ \hline
A & Device to Host & Hight& 126 MB/s\\ \hline
B & Host to Device & 10 Gb& 858 MB/s\\ \hline
B & Device to Host & 10 Gb& 843 MB/s\\ \hline
\end{tabular}\end{center}\end{table}

@@

The first of them was {\tt MonteCarloMultigpu} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of Figure~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.
% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/aws-mont1.png}
  \caption{NVIDIA SDK {\tt MonteCarloMultiGPU} execution using local and remote GPUs.}
  \label{fig:mont-opt}
\end{figure}
